---
title: "Spain is in the final!"
author: "Håvard Strand"
date: "last-modified"
categories: [knockout]
execute:
  echo: false
---

# Spain outplays France

Does it pay off to score first in this tournament? Spain came back against France after the French took the lead. 

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```


```{r knock_49, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}

invisible(Sys.setlocale())
poeng_prev <- tbl_df(read.csv("details48.csv", sep=";", header = FALSE, encoding = "utf-8"))
poeng_prev$total_prev <- poeng_prev$V2 + poeng_prev$V3 + poeng_prev$V4
poeng_prev <- poeng_prev %>% select(V1, total_prev)

poeng <- tbl_df(read.csv("details49.csv", sep=";", header = FALSE))

poeng$total <- poeng$V2 + poeng$V3 + poeng$V4

poeng <- inner_join(poeng, poeng_prev, by="V1")
poeng$diff <- poeng$total - poeng$total_prev

poeng <- rename(poeng, V35 = V4)
poeng <- rename(poeng, V34 = V3)
poeng <- rename(poeng, V36 = V2)
poeng$V34 <-poeng$V34 - poeng$diff


long_pong <- poeng %>% select(V1, V34, V35, V36, total, diff)  %>% gather(key = V, -V1, -total, value = poeng) %>% arrange(V)

invisible(Sys.setlocale())
ggplot(data = long_pong, aes(x = reorder(V1, total), y=poeng, fill = V)) + 
  geom_bar(stat = "identity") +
  coord_flip() +
  geom_text(aes(V1, 0, label = total), hjust = -0.50, size = 5) +
  ylab("Points") +
  xlab(" ") +
  scale_fill_manual(values=c("#AAAAAA", "#990000", "#E69F00", "#56B4E9"), 
                    name="Origin",
                    breaks=c("V36", "V35", "V34", "diff"),
                    labels=c("Group Stage", "Qualitative", "Knockout Stage", "Since Last")) +
  theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold")) +
  theme(legend.title=element_text(size=18), 
    legend.text=element_text(size=18))

```

Nine of us had Spain in the final, which is a prerequisite for getting 200 points in the final. If Spain wins, the winner must be one of the individuals who had Spain in the final. There are 7 points between Felix and Vegard. In between there is Anna, but her winner is regrettably out of the tournament. Importantly, 7 points is less than the 30 points awarded for each correct answer for the 15 questions. 



