---
title: "Group E ended in stalemate"
author: "Håvard Strand"
date: "last-modified"
categories: [update]
execute:
  echo: false
---

# Wednesday 26th June 2024, We all love Romania

Ukraina is out and Romania has won the hearts of football fans all over the world. Belgium was a dissapointment of sorts, but where England barely had a pulse, Belgium had three goals disallowed by VAR. Quantitative indicators does not always conway the whole truth, despite Dagfinn's insistence that it does. 







```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```



```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
#| warning: false

invisible(capture.output(Sys.setlocale()))
nettverk <- readr::read_delim("res34.csv", delim=";", col_names = FALSE, locale = locale(encoding = "UTF-8"))
leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff <- hbar$X35-hbar$X33

ggplot(hbar, aes(x=reorder(X1, X35), y=X35, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 510)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = X35), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))
```
Dagfinn remain in the lead, but Jacob, Maiken, Jostein, Vegard, Kristoffer, Chistian and Øyvind are within a game's distance. Olav outperformed everyone today and shoots up the standings.

```{r graph2, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
