---
title: "Denmark - England 1-1"
author: "Håvard Strand"
date: "last-modified"
categories: [update]
execute:
  echo: false
---

# Tuesday 19th June 2024, Denmark - England 1-1

Both Denmark and England are most probably thorugh with this result, but questions continue regarding England's favorite status. 


```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

Vegard is now in the lead. With three games in a row ending in a draw, the organizing comittee is not surprised to see Jon making a quick climb up the scale. However, Dagfinn, Jan Erling and Halvard are all within striking distance. 



```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
#| warning: false

invisible(capture.output(Sys.setlocale()))
nettverk <- readr::read_delim("res17.csv", delim=";", col_names = FALSE, locale = locale(encoding = "UTF-8"))
leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff <- hbar$X18-hbar$X17

ggplot(hbar, aes(x=reorder(X1, X18), y=X18, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 360)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = X18), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
