---
title: "Group B was a close call"
author: "Håvard Strand"
date: "last-modified"
categories: [update]
execute:
  echo: false
---

# Monday 24rd June 2024, Group B is decided. Albania is out, Croatia hangs from a cliff

Spain B beat Albania, while Italy claimed a point with the penultimate touch of the game. We feel with Croatia. 

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

It is shocking to see how many of us that had both outcomes tonight. In fact, except for Nina, Kristoffer and myself, everyone can feel good about their predictions tonight.


```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
#| warning: false

invisible(capture.output(Sys.setlocale()))
nettverk <- readr::read_delim("res28.csv", delim=";", col_names = FALSE, locale = locale(encoding = "UTF-8"))
leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff <- hbar$X29-hbar$X27

ggplot(hbar, aes(x=reorder(X1, X29), y=X29, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 490)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = X29), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))
```
Dagfinn is in the lead, Christian, Maiken and Vegard are close behind and the cup holder Øyvind has climbed back in contention.

