---
title: "End of the group stage"
author: "Håvard Strand"
date: "last-modified"
categories: [update]
execute:
  echo: false
---

# Wednesday 26th June 2024, The group stage is over, and we split a lot of points

Georgia beating Portugal 2-0 was not the most common guess around, but it happened. Turkey beating Czeck Republic was less of a surprise. Hard to know how we fared, as these were the final games of the group stage, and all the games for the first knockout round are ready. Which means that a lot of points are distributed and a new leader emerges. Or rather, re-emerges.






```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```



```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
#| warning: false

invisible(capture.output(Sys.setlocale()))
nettverk <- readr::read_delim("res36.csv", delim=";", col_names = FALSE, locale = locale(encoding = "UTF-8"))
leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff <- hbar$X37-hbar$X35

ggplot(hbar, aes(x=reorder(X1, X37), y=X37, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 910)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = X37), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))
```
Øyvind came from behind with a massive score. The details must be analyzed in daylight, but it seems Øyvind and Philipp had 14 out of 16 teams for the knockout round, and 9 of them in the correct spot. As it stands, Øyvind is 41 points ahead of Dagfinn, With Jostein in third. 

```{r graph2, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
