---
<<<<<<< HEAD
title: "The average age of the Danish starting 11"
=======
title: "What was that?"
>>>>>>> 660aba316b219af8a7ac896bdc55c4f5a82a87d9
author: "Håvard Strand"
date: "last-modified"
categories: [update]
execute:
  echo: false
---

<<<<<<< HEAD
# How old were the Danish starting 11?





=======
# Monday 17th June 2024, Belgium lost to Slovaika
>>>>>>> 660aba316b219af8a7ac896bdc55c4f5a82a87d9


```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

The color of love, the color of blood
The color of roses, the color of mud
The color of passion, the color of fire
The color of anger, the color of desire
The color of danger, the color of heat
The color of victory, the color of defeat
The color of life, the color of death
The color of courage, the color of breath
The color of war, the color of peace
The color of joy, the color of grief
The color of power, the color of pain
The color of sunshine, the color of rain
The color of beauty, the color of sin
The color of the world we live in
The color of red, so bold and bright
The color of day, the color of night

So, for the first time ever, or at least as far as I know, we have had a totally unforeseen outcome. Belgium lost to Slovaika.

The red color in the graph tells us how much each of us lost in the prediction. The more red, the more we lost. My 4-1 bet cost me 16 points.


```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
#| warning: false

invisible(capture.output(Sys.setlocale()))
nettverk <- readr::read_delim("res9.csv", delim=";", col_names = FALSE, locale = locale(encoding = "UTF-8"))
leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff <- hbar$X10-hbar$X9


ggplot(hbar, aes(x=reorder(X1, X10), y=X10, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 230)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = X10), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))
```
Halvard lost less than Øyvind, and the two share the top spot. Dagfinn also closed in on the top. Felix did the opposite and there is again a significant gap.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
