---
title: "The average age of the Danish starting 11"
author: "Håvard Strand"
date: "last-modified"
categories: [update]
execute:
  echo: false
editor: 
  markdown: 
    wrap: 72
---

# How old were the Danish starting 11?

The following players

|     |                       |                            |
|-----|-----------------------|----------------------------|
|     |                       |                            |
| 1   | Kasper Schmeichel     | 5 November 1986 (aged 37)  |
|     |                       |                            |
| 2   | Joachim Andersen      | 31 May 1996 (aged 28)      |
|     |                       |                            |
| 3   | Jannik Vestergaard    | 3 August 1992 (aged 31)    |
|     |                       |                            |
| 6   | Andreas Christensen   | 10 April 1996 (aged 28)    |
|     |                       |                            |
| 9   | Rasmus Højlund        | 4 February 2003 (aged 21)  |
|     |                       |                            |
| 10  | Christian Eriksen     | 14 February 1992 (aged 32) |
|     |                       |                            |
| 17  | Victor Kristiansen    | 16 December 2002 (aged 21) |
|     |                       |                            |
| 18  | Alexander Bah         | 9 December 1997 (aged 26)  |
|     |                       |                            |
| 19  | Jonas Wind            | 7 February 1999 (aged 25)  |
|     |                       |                            |
| 21  | Morten Hjulmand       | 25 June 1999 (aged 24)     |
|     |                       |                            |
| 23  | Pierre-Emile Højbjerg | 5 August 1995 (aged 28)    |
|     |                       |                            |

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```


```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
#| warning: false

invisible(capture.output(Sys.setlocale()))
nettverk <- readr::read_delim("res9.csv", delim=";", col_names = FALSE, locale = locale(encoding = "UTF-8"))
leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff <- hbar$X10-hbar$X9


ggplot(hbar, aes(x=reorder(X1, X10), y=X10, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 230)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = X10), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))
```

Halvard lost less than Øyvind, and the two share the top spot. Dagfinn
also closed in on the top. Felix did the opposite and there is again a
significant gap.

\`\`\`{r, echo=FALSE, warning=FALSE, message=FALSE}
