---
title: "Slovakia - Ukraine 1-2"
author: "Håvard Strand"
date: "last-modified"
categories: [update]
execute:
  echo: false
---

# Tuesday 19th June 2024, Slovakia - Ukraine 1-2

Group E is turning into a heated affair. If Belgium wins against Romania tomorrow, it is a matter of goal difference. If Belgium fails to win, they are in trouble, which has consequences for our competition.


```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

Most of us did not see this coming. In fact, only 11 gained points from this game. Vegard remain in a clear lead, but Kristoffer, Jacob and Christian gained significantly. Well done!



```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
#| warning: false

invisible(capture.output(Sys.setlocale()))
nettverk <- readr::read_delim("res19.csv", delim=";", col_names = FALSE, locale = locale(encoding = "UTF-8"))
leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff <- hbar$X20-hbar$X19

ggplot(hbar, aes(x=reorder(X1, X20), y=X20, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 380)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = X20), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
